Toxic code snippets on Stack Overflow

### 2017-10-22 cloverflow-tse/cloverflow.tex
Fixed most of the FIXMEs.

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
Online code clones are code fragments that are copied from software projects or
online sources to Stack Overflow as examples in questions and answers. % They
Due to an absence of a checking mechanism after the code has been copied to
Stack Overflow, they can become toxic code snippets, i.e.~ they suffer from
being outdated or violating the original software license. We present a study
incorporating several state-of-the-art tools and techniques to automatically
extract and filter detected online clone pairs between 72,365 Java code snippets
on Stack Overflow and 111 Java open source projects in the curated Qualitas
corpus. We discovered and analysed 2,302 non-trivial online clone candidates.
Our investigation of the online clone pairs revealed strong evidence that 154
clones have been copied from a Qualitas project to Stack Overflow.  We found 101
of them (66\%) to be outdated and potentially harmful for reuse.  Furthermore,
we found 214 code snippets on Stack Overflow that violate the license of their
original software. We surveyed 201 high-reputation Stack Overflow answerers
(33\% response rate) and found that 69 of them (FIXME\%) have never been notified of
outdated code in the answers and 26 of them (FIXME\%) rarely or never fix the outdated
code. Only 3 answerers explicitly include software license in their answers and
138 answerers (FIXME\%) never check for licensing conflicts between their copied code
snippets and Stack Overflow's CC BY-SA 3.0.
\end{abstract}

@@

The second motivating example of outdated online code clones with more
disrupting changes than the first one  can be found in an answer to a Stack
Overflow question regarding how to format files sizes in a human readable form.
\Cref{fig:before-after_2} shows---on the left---a code snippet to perform the
task from the {\small{\texttt{StringUtils}}} class in \textsf{Hadoop}. The code snippet on the
right shows another version of the same method, but at this time extracted from
the latest version of \textsf{Hadoop}. We can see that
they are totally different. The {\small{\texttt{humanReadableInt}}} method is
rewritten on February 5, 2013 to solve an issue of a race condition
(issue no.~HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
\FIXME{I don't understand the following:} The absence of Apache v.2.0 license also occurs after the snippet is posted on 
Stack Overflow.

@@

\textbf{Clone Detection Configuration: } We are aware of effects of
configurations to clone detection results and the importance of searching for
optimised configurations in empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016, emse}. However,
considering the massive size of the two datasets and the search space of at
least 15 Simian and 3 SourcererCC parameters, we are unable to search for the
best configurations of the tools. Thus, we decided to configure Simian and
SourcererCC based on their established default configurations chosen by the
tools' creators as depicted in \Cref{tab:clone_config}. 
\FIXME{Something is not right: First it says that variable renaming is
  disabled, and later it is said that SourcererCC uses renaming.}
All variable renaming are disabled to decrease the number of
false positives since we aim for finding clones that are copied from open source
projects with minimal modifications. The two clone detectors complement each
other by having Simian detecting literal copies of code snippets (type-1) and SourcererCC
detecting clones with renaming and added/deleted statements (type-2, type-3). We made sure that they 
detected only non-trivial clones by increasing the minimum clone size to ten
lines.
%(denoted as \textit{D}), and (2)~the discovered configurations for
%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
%of optimising clone detectors' configurations based on clone agreement
%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
%In total, we have four configurations: Simian with the default
%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
%NiCad with the default configuration ($N_D$)
%and NiCad with the EvaClone configuration ($N_E$).

@@

\textbf{Manual investigation:} 
To mitigate the human error, we deployed two persons in the manual clone
investigation process. The first author, who is a research student working on
clone detection research for three years, and the third author, who is a
software engineering research student and familiar with code clones, took the
role of the investigators performing a manual validation and classification of
the merged clone pairs. The two investigators separately went through each clone
pair candidate, looked at the clones, and decided if they are a true positive or
a false positive and classified them into an appropriate pattern. After the
validation, the results from the two investigators were compared and 607 (26\%)
conflicts were discussed and resolved. There are 145 conflicts caused by
one investigator being more careful than the other and able to find evidence of 
copying while the other could not. They result in a better classification,
 i.e.~from UD to QS or EX.~\FIXME{Report \% of conflicts
 between TP vs.~FP classifications first, and then about evidence.}
%There were three conflicts where the two
%investigators could not find a consensus and the third author was involved for
%the final judgement.

@@

		SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\

		EX & Cloned from an external source \textit{X} (X $\rightarrow$ S). \\

@@

\begin{table}
	\centering
	\caption{License mapping of online clones (file-level)
          \FIXME{Change order of columns, Qualitas before SO}}
	\label{tab:license_abc}
	%\small
	\resizebox{\linewidth}{!}{
		\begin{tabular}{lp{2.3cm}p{2.3cm}rrr}
			\toprule
			Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
			\midrule
			Compatible 
			& Apache-2 & Apache-2 & 1 & & \\ 
			& EPLv1 & EPLv1 & 2 & & 1 \\ 
			& Proprietary & Proprietary & & 2 & \\ 
			& Sun Microsystems & Sun Microsystems & & 3 & \\ 
			& No license & No license & 20 & 9 & 2 \\ 
			& CC BY-SA 3.0 & No license & & 1 & \\
			\midrule
			\multicolumn{3}{l}{Total} & 23 & 15 & 3 \\
			\midrule
			Incompat. 
			& No license & AGPLv3/3+ & 1 & & 4 \\
			& No license & Apache-2 & 46 & 14 & 12 \\  
			& No license & BSD/BSD3 & 4 & & 1 \\ 
			& No license & CDDL or GPLv2 & & & 6 \\ 
			& No license & EPLv1 & 10 & & 6 \\
			& No license & GPLv2+/3+ & 8 & 48 & 7 \\ 
			& No license & LesserGPLv2.1+/3+ & 16 & & 9 \\ 			
			& No license & MPLv1.1 & & & 1 \\ 
			& No license & Oracle & & 3 \\ 
			& No license & Proprietary & & 1 & 2 \\ 
			& No license & Sun Microsystems & & 1 & 2 \\ 
			& No license & Unknown & & 11 & \\
			& New BSD3 & LesserGPLv2.1+ & 1 & & \\ 
			\midrule
			\multicolumn{3}{l}{Total} & 86 & 78 & 50 \\
			\bottomrule
		\end{tabular} 
	}
\end{table}

@@

\subsubsection{General Information}
As shown in \Cref{tab:survey_exp}, the majority of the answerers are experienced
developers with more than 10 years of experience (55.4\%) or between 5 to 10
years (28.7\%). They are active users and regularly answer questions. 49
participants (FIXME\%) answer questions on Stack Overflow every day.

>>>>

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
Online code clones are code fragments that are copied from software projects or
online sources to Stack Overflow as examples in questions and answers. % They
Due to an absence of a checking mechanism after the code has been copied to
Stack Overflow, they can become toxic code snippets, i.e.~ they suffer from
being outdated or violating the original software license. We present a study
incorporating several state-of-the-art tools and techniques to automatically
extract and filter detected online clone pairs between 72,365 Java code snippets
on Stack Overflow and 111 Java open source projects in the curated Qualitas
corpus. We discovered and analysed 2,302 non-trivial online clone candidates.
Our investigation of the online clone pairs revealed strong evidence that 154
clones have been copied from a Qualitas project to Stack Overflow.  We found 101
of them (66\%) to be outdated and potentially harmful for reuse.  Furthermore,
we found 214 code snippets on Stack Overflow that violate the license of their
original software. We surveyed 201 high-reputation Stack Overflow answerers
(33\% response rate) and found that 69 of them (34.5\%) have never been notified of
outdated code in the answers and 26 of them (19.8\%) rarely or never fix the outdated
code. Only 3 answerers explicitly include software license in their answers and
138 answerers (69\%) never check for licensing conflicts between their copied code
snippets and Stack Overflow's CC BY-SA 3.0.
\end{abstract}

@@

The second motivating example of outdated online code clones with more
disrupting changes than the first one  can be found in an answer to a Stack
Overflow question regarding how to format files sizes in a human readable form.
\Cref{fig:before-after_2} shows---on the left---a code snippet to perform the
task from the {\small{\texttt{StringUtils}}} class in \textsf{Hadoop}. The code snippet on the
right shows another version of the same method, but at this time extracted from
the latest version of \textsf{Hadoop}. We can see that
they are totally different. The {\small{\texttt{humanReadableInt}}} method is
rewritten on February 5, 2013 to solve an issue of a race condition
(issue no.~HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
Similar to the first example, the clone code snippet on Stack Overflow does not 
include its original Apache v.2.0 license.
%\FIXME{I don't understand the following:} The absence of Apache v.2.0 license also occurs after the snippet is posted on 
%Stack Overflow.

@@

\textbf{Clone Detection Configuration: } We are aware of effects of
configurations to clone detection results and the importance of searching for
optimised configurations in empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016, emse}. However,
considering the massive size of the two datasets and the search space of at
least 15 Simian and 3 SourcererCC parameters, we are unable to search for the
best configurations of the tools. Thus, we decided to configure Simian and
SourcererCC based on their established default configurations chosen by the
tools' creators as depicted in \Cref{tab:clone_config}. 
%\FIXME{Something is not right: First it says that variable renaming is
%  disabled, and later it is said that SourcererCC uses renaming.}
%All variable renaming are disabled to decrease the number of
%false positives since we aim for finding clones that are copied from open source
%projects with minimal modifications. 
The two clone detectors complement each
other by having Simian detecting literal copies of code snippets (type-1) and SourcererCC
detecting clones with renaming and added/deleted statements (type-2, type-3). We made sure that they 
detected only non-trivial clones by increasing the minimum clone size to ten
lines.
%(denoted as \textit{D}), and (2)~the discovered configurations for
%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
%of optimising clone detectors' configurations based on clone agreement
%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
%In total, we have four configurations: Simian with the default
%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
%NiCad with the default configuration ($N_D$)
%and NiCad with the EvaClone configuration ($N_E$).

@@

\textbf{Manual investigation:} 
To mitigate the human error, we deployed two persons in the manual clone
investigation process. The first author, who is a research student working on
clone detection research for three years, and the third author, who is a
software engineering research student and familiar with code clones, took the
role of the investigators performing a manual validation and classification of
the merged clone pairs. The two investigators separately went through each clone
pair candidate, looked at the clones, and decided if they are a true positive or
a false positive and classified them into an appropriate pattern. After the
validation, the results from the two investigators were compared. 
%and 607 (26\%)
%conflicts were discussed and resolved. 
There are 338 (15\%) conflicts between 
true and false clones (QS, SQ, EX, UD, BP, IN vs.~AC). The other 270 pairs (12\%) are 
conflicts in the classification of
the true clone pairs. Among these pairs, 145 conflicts were caused by
one investigator being more careful than the other and able to find evidence of 
copying while the other could not. They result in a better classification,
 i.e.~from UD to QS or EX.
%~\FIXME{Report \% of conflicts
% between TP vs.~FP classifications first, and then about evidence.}
%There were three conflicts where the two
%investigators could not find a consensus and the third author was involved for
%the final judgement.

@@

		SQ & Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\

		EX & Cloned from an external source \textit{X} to Stack Overflow\newline (X $\rightarrow$ S). \\

@@

\begin{table}
	\centering
	\caption{License mapping of online clones (file-level)}
	\label{tab:license_abc}
	%\small
	\resizebox{\linewidth}{!}{
		\begin{tabular}{lp{2.3cm}p{2.3cm}rrr}
			\toprule
			Type & Qualitas & Stack Overflow\newline (CC BY-NC-SA)& QS & EX & UD \\
			\midrule
			Compatible 
			& Apache-2 & Apache-2 & 1 & & \\ 
			& EPLv1 & EPLv1 & 2 & & 1 \\ 
			& Proprietary & Proprietary & & 2 & \\ 
			& Sun Microsystems & Sun Microsystems & & 3 & \\ 
			& No license & No license & 20 & 9 & 2 \\ 
			& No license & CC BY-SA 3.0 & & 1 & \\
			\midrule
			\multicolumn{3}{l}{Total} & 23 & 15 & 3 \\
			\midrule
			Incompat. 
			& AGPLv3/3+ & No license & 1 & & 4 \\
			& Apache-2 & No license & 46 & 14 & 12 \\  
			& BSD/BSD3 & No license & 4 & & 1 \\ 
			& CDDL or GPLv2 & No license & & & 6 \\ 
			& EPLv1 & No license & 10 & & 6 \\
			& GPLv2+/3+ & No license & 8 & 48 & 7 \\ 
			& LesserGPLv2.1+/3+ & No license & 16 & & 9 \\ 			
			& MPLv1.1 & No license & & & 1 \\ 
			& Oracle & No license & & 3 \\ 
			& Proprietary & No license & & 1 & 2 \\ 
			& Sun Microsystems & No license & & 1 & 2 \\ 
			& Unknown & No license & & 11 & \\
			& LesserGPLv2.1+ & New BSD3 & 1 & & \\ 
			\midrule
			\multicolumn{3}{l}{Total} & 86 & 78 & 50 \\
			\bottomrule
		\end{tabular} 
	}
\end{table}

@@

\subsubsection{General Information}
As shown in \Cref{tab:survey_exp}, the majority of the answerers are experienced
developers with more than 10 years of experience (55.4\%) or between 5 to 10
years (28.7\%). They are active users and regularly answer questions. 49
participants (24\%) answer questions on Stack Overflow every day.
